Visualizations for the manuscript

### 2022-05-16 metanalysis_visualization/manuscript_Figures.Rmd
coeff label changed to coefficient and feeding and eating disorders now eating disorder

pvalues_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coeffs differences: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

pvalues_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coeffs differences: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

>>>>

pvalues_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coefficient difference: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

pvalues_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coefficient difference: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )
